Enter our title here

### 2017-12-24 manuscript.tex
made edits to manuscript

When starting to create a DataCamp course, it is helpful to view code from pre-existing community courses which can be found on GitHub.
You can use these files as a guide to build your own course or duplicate the repository and tailor the content to fit specific needs.
The DataCamp github repository contains links to the code for several available courses; one of the most helpful when starting to build a course 
is \url{https://github.com/datacamp/courses-intro-to-r} which contains the source files for the `Intoduction to R' course.

Educators are able to edit their courses in a number of ways but the 'Teach Editor' located in the teach dashboard is the
most straight forward editor. The 'Teach Editor' is specifically designed to make the creation process of a DataCamp course
as painless as possible, allowing writers to edit, preview, save changes and synchronize to a GitHub repository. Editing can
also be done through GitHub's online editor and through git locally but these methods do not allow for automatic content
viewing.

DataCamp courses may contain 3 different types of exercises: Normal, Multiple choice, and video.

A \texttt{NormalExercise} is an exercise that prompts a user to submit code. The components of this include: lesson section, instructions, pre-exercise code, sample code, hint, solution and a submission correctness testing coded (SCT). However, the interface for students (or the 'Preview
mode) only includes the lesson, Instructions, R script panel and a R console panel (Figure~\ref{fig:code1}).

\begin{figure}
\caption{This code does this}
\begin{verbatim}
--- type:NormalExercise lang:r xp:100 skills:1 key:9a4fea2da
## Visualizing quantitative data in R

@@

Whenever a new exercise is added, DataCamp automatically produces the top line in the editor. The header specifies the type
of exercise \texttt{type}, language \texttt{lang}, available points \texttt{xp}, skills learned \texttt{skills} and a \texttt{key}. The key acts as a unique
identifier for that exercise, allowing you to modify the content without losing any student data. Currently, DataCamp offers
eight different skills which are defined by numbers 1-8. The skills and their corresponding numbers can be found in the DataCamp
documentation \url{https://www.datacamp.com/teach/documentation#tab_gamification}. 
In the above exercise code, the \texttt{type} is Normal, the language is R, the available points is 100 and the skills learned is 1 (which 
corresponds to R Programming). DataCamp assigns 100 points to normal coding exercises but this value can be modified depending on
difficulty level. After students have completed the exercise, they can check their personal profile to see how many points they earned.

In the `Assignment' portion of the exercise, instructors can add additional information about the assignment that will help
students understand and complete the instructions. The `Instructions' section contains the actual task the student is
asked to execute; instructors can also include a `Hint' for extra guidence (optional). The 'pre-exercise code' sets up the workspace for 
the student; this section will contain code to import data sets, install packages and any other operation that you want to be available to
students. The 'sample code' section contains code or notes that students view in the R script panel. Students also use the R script panel to write
the code that solves the tasks in the instructions. The correct answer to an exercise is coded in the 'solution' section
and when the student clicks the `Submit Code' button, their answer passes through the SCT code where their code is checked for errors.

The submission correctness testing code (or SCT) automatically assesses if the correct code was submitted. If a student submits an 
incorrect answer, they will receive immediate feedback on what they are doing wrong and the system will guide them to the right answer.
Instructors can use the default feedback that DataCamp automatically generates or write their own custom messages. For example, figure blank
contains the default feedback for an incorrect submission of the \texttt{hist()} function.

\begin{figure}
\caption{This code does this}
\begin{Verbatim}[frame=single]

@@

The default feedback is meaningful and specific; most of the time custom 
messages are not necessary unless there is a common problem that student are struggling with in which more unique feedback is necessary. 
DataCamp provides a helpful R package called 'testwhat' which acts as a guide to writing and using SCTs (this can be accessed on DataCamp's GitHub 
repository: \url{https://github.com/datacamp/testwhat/wiki}. 
'testwhat' contains functions that can test different types of problems including loops, object definitions, printed output, functions, ect.
The submission correctness testing code compares the ideal answer (from the solution) to the students answer. Different
arguements can be added to the test functions to alter the testing process and automatic feedback. (**do I cite datacamp website here?**)

>>>>

When starting to create a DataCamp course, it is helpful to view code from pre-existing community courses which can be found on GitHub.
You can use these files as a guide to build your own course or duplicate the repository and tailor the content to fit specific needs.
The DataCamp github repository contains links to the code for several available courses; one of the most helpful when starting to build a course 
is \url{https://github.com/datacamp/courses-intro-to-r} which contains the source files for the \textit{Intoduction to R} course.

Educators are able to edit their courses in a number of ways but the \texttt{Teach Editor} located in the teach dashboard is the
most straight forward editor. The \texttt{Teach Editor} is specifically designed to make the creation process of a DataCamp course
as painless as possible, allowing writers to edit, preview, save changes and synchronize to a GitHub repository. Editing can
also be done through GitHub's online editor and through git locally but these methods do not allow for automatic content
viewing.

DataCamp courses may contain 3 different types of exercises: Normal coding exercises, Multiple choice, and Video.

A \texttt{NormalExercise} is an exercise that prompts a user to submit code. The components of this include: lesson section, instructions, pre-exercise code, sample code, hint, solution and a submission correctness testing code (SCT). (add reference to teach editor code) However, the interface for students (or the \texttt{Preview}
mode) only includes the lesson, instructions, R script panel and a R console panel (Figure~\ref{fig:code1}).

\begin{figure}
\caption{Teach Editor Interface}
\begin{verbatim}
--- type:NormalExercise lang:r xp:100 skills:1 key:9a4fea2da
## Visualizing quantitative data in R

@@

Whenever a new exercise is added, DataCamp automatically produces the top line (header) in the editor. The header specifies the type
of exercise \texttt{type}, language \texttt{lang}, available points \texttt{xp}, skills learned \texttt{skills} and a \texttt{key}. The key acts as a unique
identifier for that exercise, allowing you to modify the content without losing any student data. Currently, DataCamp offers
eight different skills which are defined by numbers 1-8. The skills and their corresponding numbers can be found in the DataCamp
documentation \url{https://www.datacamp.com/teach/documentation#tab_gamification}. 
In the above exercise code (refer to teach editor code), the \texttt{type} is Normal, the language is R, the available points is 100 and the skills learned is 1 (which 
corresponds to R Programming). DataCamp assigns 100 points to normal coding exercises but this value can be modified depending on
difficulty level. After students have completed the exercise, they can check their personal profile to see how many points they earned.

In the \textit{Assignment} portion of the exercise (not labeled but below the header), instructors can add additional information about the assignment that will help
students understand and complete the instructions. The \textit{instructions} section contains the actual task the student is
asked to execute; instructors can also include a \textit{hint} for extra guidence (optional). The \textit{pre-exercise code} sets up the workspace for 
the student; this section will contain code to import data sets, install packages and any other operation that you want to be available to
students. The \textit{sample code} section contains code or notes that students view in the R script panel. Students also use the R script panel to write
the code that solves the tasks in the instructions. The correct answer to an exercise is coded in the \textit{solution} section
and when the student clicks the \texttt{Submit Code} button, their answer passes through the SCT code where their code is checked for errors.

The submission correctness testing code (or SCT) automatically assesses if the correct code was submitted. If a student submits an 
incorrect answer, they will receive immediate feedback on what they are doing wrong and the system will guide them to the right answer.
Instructors can use the default feedback that DataCamp automatically generates or write their own custom messages. For example, figure blank
contains the default feedback for a few possible incorrect submissions of the \texttt{hist()} function.

\begin{figure}
\caption{Examples of DataCamps Default Feedback}
\begin{Verbatim}[frame=single]

@@

The default feedback is meaningful and specific; most of the time custom 
messages are not necessary unless there is a common problem that student are struggling with in which more unique feedback is necessary. 
DataCamp provides a helpful R package called \textit{testwhat} which acts as a guide to writing and using SCTs (this can be accessed on DataCamp's GitHub 
repository: \url{https://github.com/datacamp/testwhat/wiki}. 
\textit{testwhat} contains functions that can test different types of problems including loops, object definitions, printed output, functions, ect.
The submission correctness testing code compares the ideal answer (from the solution) to the students answer. Different
arguements can be added to the test functions to alter the testing process and automatic feedback. (**do I cite datacamp website here?**)
